Frequency of dwarf and massive galaxy pairs in the IllustrisTNG cosmological simulation

### 2023-02-11 paper/pears.tex
final edits for the day to the velocity results sec.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample selection}\label{sec:methods}
Our sample data was obtained using a strict set of selection criteria, as outlined in this section.
In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulations utilized in this study.
Sec.~\ref{sec:methods-am} explains the abudance matching prescription used to associate stellar masses with the dark matter subhalos.
Sec.~\ref{sec:methods-crit} provides a detailed outline of our selection criteria and process for picking pairs.
Finally, Sec.~\ref{sec:methods-counts} gives an overview of the properties of our sample.

@@

% details of Illustris and Illustris TNG
The \textit{Illustris Project} ~\citep{vogelsberger14A,nelson15} and \textit{IllustrisTNG Project}~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} are a set of N-body and hydrodynamic cosmological simulations which are perfectly suited for such a study. 
We use the dark matter only and full hydrodynamic runs of both the \ill-1 and \tng100-1 simulations to explore the connection between pairs and baryonic processes. 
Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of roughly $100^3$ Mpc$^3$. 
The \ill{} simulations follow a cosmology consistent with \textit{WMAP-9}~\citep{hinshaw13}, while the \tng{} simulations are consistent with \textit{Planck2015}~\citep{Planck2015}.
Specifically, we use the \textit{Illustris-1-Dark}, \textit{Illustris-1}, \textit{TNG100-1-Dark}, and \textit{TNG100-1} simulations (hereafter \illd, \illh, \tngd, and \tngh{} respectively, see Table~\ref{table:sim} for details).

@@

% subfind, sublink, and groups and subhalos
We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm ~\citep{springel01,dolag09}. 
These catalogs consist of halos (or "groups"), defined using the Friends-of-Friends (FoF) algorithm~\citep{davis85} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures.
We also use the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data, in order to trace the mass growth and merger histories of our subhalos.

\begin{table*}[htb]
\begin{tabular}{l|llll}
 & \illd & \illh & \tngd & \tngh\\\hline\hline
 L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\
m$_{\rm gas}$ & -- & $1.3\times 10^{6}$ & -- & $1.4\times 10^{6}$ \\\hline
\end{tabular}
\caption{\label{table:sim}Parameters of the Illustris simulations used in this analysis.}
\end{table*}

@@

% How do we utilize it? 
In particular, we use the abundance matching relationship presented in~\citet{moster13}, which provides an analytic recipe to paint stellar masses onto dark matter halos. 
The~\citet{moster13} relationship is a redshift-evolving function of the halo mass, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
\kc{why moster instead of another AM relationship? most closely represent data at lower mass? }

@@

Thus, we treat each of the subhalos as centrals according to the~\citet{moster13} prescription, using the current snapshot redshift and the peak halo mass of the subhalo to calculate the stellar mass. 
This additionally allows us remain robust to scenarios in which a secondary may have formed most of its stars, and then lost a significant portion of its dark matter content through tidal interactions with a primary, but will retain the bulk of its stellar content.

@@

% equivalent snapshot table
\begin{table*}[]
  \centering
  \begin{tabular}{l|cc|cccc} % increase this to 7 columns
    \hline \hline
   & \multicolumn{2}{c|}{Snapshot number} & \multicolumn{4}{c}{Number of primaries}\\
   & \ill & \tng  & \illd & \illh & \tngd & \tngh \\ 
  \hline
  z = 0   &   135  &   99   & $11431.5_{-24.42}^{68.38}$ & $12650.0_{-25.84}^{46.84}$ & $13255.0_{-32.60}^{56.72}$ & $12035.0_{-69.24}^{20.36}$\\
  z = 1   &   85   &   50   &  $14769.0_{-30.24}^{47.28}$ & $16568.0_{-32.20}^{69.60}$ & $17445.5_{-40.86}^{51.90}$ & $15946.5_{-59.38}^{39.22}$ \\
  z = 2   &   68   &   33   &  $12602.5_{-31.98}^{45.94}$ & $14174.0_{-12.48}^{62.32}$ & $15413.5_{-34.62}^{28.86}$ & $14334.0_{-29.44}^{45.24}$ \\
  z = 3   &   60   &   25   &     $8533.5_{-54.50}^{39.46}$ & $9390.0_{-63.40}^{41.32}$ & $10901.0_{-44.64}^{46.56}$ & $10106.5_{-47.90}^{39.74}$  \\
  % z = 3.7   &   54   &   21   \\
  \hline \hline
  \end{tabular}
  \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the median number dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations. \kc{fill in with numbers after doing more realizations} \kc{include takeaway}}
  \end{table*}

  \begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{counts_1000.png}
    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.
    Shaded regions show the $1^{\rm st}$ and 99$^{\rm th}$ percentile spread of the medians of all realizations. 
    There are approximately 8 times as many dwarf primaries as massive primaries. 
    % dwarf galaxies
    The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$. The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
    % Massive galaxies (right)
    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$. 
    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off. At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column). Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$. The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
    \label{fig:counts}
  \end{figure*}

  \begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{stellarmass_distribution_1000.png}
    \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs. Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$. Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left). 
    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
    \label{fig:massratio}
  \end{figure*}

@@

\subsection{Pair fraction}\label{sec:results-frac}
Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.

\label{sec:results}
\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{pairratio_1000.png}
  \caption{
    % Top plots ~
    (Top) Median fraction of dwarf or massive primaries with a major or minor companion by stellar mass. 
    Shaded regions show the $1$-$99$ percentile range of the median pair fractions of each realization. 
      % massive pairs
    The fraction of massive primaries (pink) with a major (left) or minor (right) companion remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 and 0.14-0.15 respectively. Between $z=0.25$ and $z=0$, the massive major pair fraction increases sharply from 0.165 to 0.207, a 25\% increase, while the minor pair fraction increases from 0.127 to 0.152, a 20\% increase.
      % dwarf pairs
    Dwarf pairs (green), on the other hand, have pair fractions that are approximately constant from $z=3-4$, but the fraction of major(minor) pairs declines monotonically from 0.126(0.111) at x=3 to just 0.041(0.034) at x=0, a 67(70)\% decrease. 
    % Bottom plots ~
  (Bottom) The median subtracted difference between the massive pair fraction and the dwarf pair fraction, with the shaded $1$-$99$ percentile range of the difference of each realization. The difference between the massive pair fraction and dwarf pair fraction increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs. This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.}
  \label{fig:pairratio}
\end{figure*}

\subsection{Kinematic evolution}\label{sec:results-kinematics}
The primary and secondary halos of each pair at each individual snapshot/redshift is separated by some physical separation and has a relative velocity of

@@

\subsubsection{Separations}
% separation vs. redshift plot
The median separations of dwarf pairs and massive pairs smoothly increases with lower redshift, regardless of pair type. 
Fig.~\ref{fig:sep} shows the median and 1-99\% range of separations for dwarf pairs and massive pairs, as well as the subtracted difference between the median separation of major pairs and of minor pairs of both mass type. 
There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger median separation offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$). 
Thus, apart from the overall scale of the separations between primary and secondary, dwarf and massive pairs exhibit similar trends as a function of time.

% separation distribution plot
Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
Each plot is normalized such that the area under an individual curve is 1.
    % the redshift evolution
All pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$ at $z=4$, but the distributions become more and more broad as $z\to0$ (note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-crit-pairs}).

The distribution profiles are similar when the scale of the x-axis for massive pair separations is twice that of the dwarf pairs. 
Pair separations at $z=0$ tend to primarily fall between $10-\sim400\,\kpc$ for dwarf pairs and   between $10-\sim1000\,\kpc$ for massive pairs. 
At $z=4$, these ranges decrease to $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs. 
    % comparing major and minor
Major and minor pairs (both dwarf pairs and massive pairs) have roughly equivalent distributions, though the distribution of minor pairs with low separations is slightly higher than the major pairs. Thus, secondary halo of minor pairs tend to live slightly closer to their primaries than the  major secondaries.

\todo{here maybe include a table? what are some values?  z=0,1,2,3,4 and pair frac, sep, vel. ?}

\subsubsection{Relative Velocities}
% velocity vs. redshift plot
We also consider the snapshot-by-snapshot instantaneous relative velocity between each primary and secondary.
We find that the median relative velocity of all pairs (dwarf and massive, major and minor) decreases with decreasing redshift, reaching a minimum at $z=0$ as seen in Fig.~\ref{fig:vel}. 
Though the velocity scales are different, the bulk behavior of dwarf pairs and massive pairs is identical.

The median velocity of a major dwarf pair decreases approximately linearly from $xx$ at $z=4$ to $xx$ at $z=0$. Likewise, the median velocity for major massive pairs decreases.
Fig.~\ref{fig:vel} also includes a panel showing the subtracted median difference at each snapshot of the minor pair from the major pair. Since minor pairs typically have slightly higher velocities than their major pair counterparts, this difference is usually $<\sim0$.

% velocity distribution plot
Fig.~\ref{fig:vel-dist}

%%% plots for kinematics
\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation_1000.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The redshift evolution of the dwarf pairs closely resembles a power law distribution across the whole redshift range from $z=0-4$.
  At $z=4$, the typical separation between major (minor) dwarf pairs is $42(38)\,\kpc$, and peaks at $z=0$ with a median separation of $128(109)\,\kpc$.
  % Massive Pairs
  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is $81(71)\,\kpc$, to $z=1$, where median separations are $171(124)\,\kpc$. The median separation rises more steeply from z=1 to z=0, peaking around $z=\sim0$ at $288\,\kpc$ and $205\,\kpc$ for major and minor massive pairs respectively.
  % Difference plots
  (Bottom) The median subtracted separation difference between major and minor pairs, and 1-99\% shaded region.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. 
    }
  \label{fig:sep}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation_distribution_1000.png}
  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines. 
  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively). However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
    }
  \label{fig:sep-dist}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{velocity_1000.png}
  \caption{
    (Top) Median relative velocity (in \kms) between the primary and secondary halos of: dwarf pairs (left, green), and massive pairs (right, pink) as a function of redshift. 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
    The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs.
    As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases as well for both dwarf and massive pairs.
    % brief describe
    The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair). 
    % Difference plot
    (Bottom) The median subtracted relative velocity difference between major and minor pairs, and 1-99\% shaded region.
    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\,\kms$ faster than major pairs.
    }
  \label{fig:vel}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample selection}\label{sec:methods}
% methods plots
  \begin{figure*}[htp]
    \centering
    \includegraphics[width=\textwidth]{counts_1000.png}
    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.
    Shaded regions show the $1^{\rm st}$ and 99$^{\rm th}$ percentile spread of the medians of all realizations. 
    There are approximately 8 times as many dwarf primaries as massive primaries. 
    % dwarf galaxies
    The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$. The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
    % Massive galaxies (right)
    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$. 
    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off. At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column). Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$. The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
    \label{fig:counts}
  \end{figure*}

  \begin{figure*}[htp]
    \centering
    \includegraphics[width=\textwidth]{stellarmass_distribution_1000.png}
    \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs. Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$. Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left). 
    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
    \label{fig:massratio}
  \end{figure*}

Our sample data was obtained using a strict set of selection criteria, as outlined in this section.
In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulations utilized in this study.
Sec.~\ref{sec:methods-am} explains the abudance matching prescription used to associate stellar masses with the dark matter subhalos.
Sec.~\ref{sec:methods-crit} provides a detailed outline of our selection criteria and process for picking pairs.
Finally, Sec.~\ref{sec:methods-counts} gives an overview of the properties of our sample.

@@

% details of Illustris and Illustris TNG
The \textit{Illustris Project} ~\citep{vogelsberger14A,nelson15} and \textit{IllustrisTNG Project}~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} are a set of N-body and hydrodynamic cosmological simulations which are perfectly suited for such a study. 
We use the dark matter only and full hydrodynamic runs of both the \ill-1 and \tng100-1 simulations to explore the connection between pairs and baryonic processes. 
Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of roughly $100^3$ Mpc$^3$. 
The \ill{} simulations follow a cosmology consistent with \textit{WMAP-9}~\citep{hinshaw2013}, while the \tng{} simulations are consistent with \textit{Planck2015}~\citep{Planck2015}.
Specifically, we use the \textit{Illustris-1-Dark}, \textit{Illustris-1}, \textit{TNG100-1-Dark}, and \textit{TNG100-1} simulations (hereafter \illd, \illh, \tngd, and \tngh{} respectively, % see Table~\ref{table:sim} for details).

@@

% subfind, sublink, and groups and subhalos
We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm ~\citep{springel2001,dolag09}. 
These catalogs consist of halos (or "groups"), defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures.
We also use the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data, in order to trace the mass growth and merger histories of our subhalos.

% \begin{table*}[htb]
% \begin{tabular}{l|llll}
%  & \illd & \illh & \tngd & \tngh\\\hline\hline
%  L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
% m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\
% m$_{\rm gas}$ & -- & $1.3\times 10^{6}$ & -- & $1.4\times 10^{6}$ \\\hline
% \end{tabular}
% \caption{\label{table:sim}Parameters of the Illustris simulations used in this analysis.}
% \end{table*}

@@

% How do we utilize it? 
In particular, we use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic recipe to paint stellar masses onto dark matter halos. 
The~\citet{Moster2013} relationship is a redshift-evolving function of the halo mass, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
\kc{why moster instead of another AM relationship? most closely represent data at lower mass? }

@@

Thus, we treat each of the subhalos as centrals according to the~\citet{Moster2013} prescription, using the current snapshot redshift and the peak halo mass of the subhalo to calculate the stellar mass. 
This additionally allows us remain robust to scenarios in which a secondary may have formed most of its stars, and then lost a significant portion of its dark matter content through tidal interactions with a primary, but will retain the bulk of its stellar content.

@@

% equivalent snapshot table
\begin{table*}[tbp]
  \centering
  \begin{tabular}{l|cc|cccc} % increase this to 7 columns
    \hline \hline
   & \multicolumn{2}{c|}{Snapshot number} & \multicolumn{4}{c}{Number of primaries}\\
   & \ill & \tng  & \illd & \illh & \tngd & \tngh \\ 
  \hline
  z = 0   &   135  &   99   & $11431.5_{-24.42}^{68.38}$ & $12650.0_{-25.84}^{46.84}$ & $13255.0_{-32.60}^{56.72}$ & $12035.0_{-69.24}^{20.36}$\\
  z = 1   &   85   &   50   &  $14769.0_{-30.24}^{47.28}$ & $16568.0_{-32.20}^{69.60}$ & $17445.5_{-40.86}^{51.90}$ & $15946.5_{-59.38}^{39.22}$ \\
  z = 2   &   68   &   33   &  $12602.5_{-31.98}^{45.94}$ & $14174.0_{-12.48}^{62.32}$ & $15413.5_{-34.62}^{28.86}$ & $14334.0_{-29.44}^{45.24}$ \\
  z = 3   &   60   &   25   &     $8533.5_{-54.50}^{39.46}$ & $9390.0_{-63.40}^{41.32}$ & $10901.0_{-44.64}^{46.56}$ & $10106.5_{-47.90}^{39.74}$  \\
  % z = 3.7   &   54   &   21   \\
  \hline \hline
  \end{tabular}
  \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the median number dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations. \kc{fill in with numbers after doing more realizations} \kc{include takeaway}}
  \end{table*}

@@

\subsection{Pair fraction}\label{sec:results-frac}
%% text on pair fraction plot
\kc{WIP} Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.

%% pair fraction plot
\label{sec:results}
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{pairratio_1000.png}
  \caption{
    % Top plots ~
    (Top) Median fraction of dwarf or massive primaries with a major or minor companion by stellar mass. 
    Shaded regions show the $1$-$99$ percentile range of the median pair fractions of each realization. 
      % massive pairs
    The fraction of massive primaries (pink) with a major (left) or minor (right) companion remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 and 0.14-0.15 respectively. Between $z=0.25$ and $z=0$, the massive major pair fraction increases sharply from 0.165 to 0.207, a 25\% increase, while the minor pair fraction increases from 0.127 to 0.152, a 20\% increase.
      % dwarf pairs
    Dwarf pairs (green), on the other hand, have pair fractions that are approximately constant from $z=3-4$, but the fraction of major(minor) pairs declines monotonically from 0.126(0.111) at x=3 to just 0.041(0.034) at x=0, a 67(70)\% decrease. 
    % Bottom plots ~
  (Bottom) The median subtracted difference between the massive pair fraction and the dwarf pair fraction, with the shaded $1$-$99$ percentile range of the difference of each realization. The difference between the massive pair fraction and dwarf pair fraction increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs. This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.}
  \label{fig:pairratio}
\end{figure*}

\subsection{Kinematic evolution}\label{sec:results-kinematics}
\kc{WIP}
The primary and secondary halos of each pair at each individual snapshot/redshift is separated by some physical separation and has a relative velocity of

@@

\subsubsection{Separations}
%% text on separation vs. redshift plot
The median separations of dwarf pairs and massive pairs smoothly increases with lower redshift, regardless of pair type. 
Fig.~\ref{fig:sep} shows the median and 1-99\% range of separations for dwarf pairs and massive pairs, as well as the subtracted difference between the median separation of major pairs and of minor pairs of both mass type. 
There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger median separation offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$). 
Thus, apart from the overall scale of the separations between primary and secondary, dwarf and massive pairs exhibit similar trends as a function of time.

%% text on separation distribution plot
Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
Each plot is normalized such that the area under an individual curve is 1.
    % the redshift evolution
All pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$ at $z=4$, but the distributions become more and more broad as $z\to0$ (note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-crit-pairs}).
\linebreak
The distribution profiles are similar when the scale of the x-axis for massive pair separations is twice that of the dwarf pairs. 
Pair separations at $z=0$ tend to primarily fall between $10-\sim400\,\kpc$ for dwarf pairs and   between $10-\sim1000\,\kpc$ for massive pairs. 
At $z=4$, these ranges decrease to $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs. 
    % comparing major and minor
Major and minor pairs (both dwarf pairs and massive pairs) have roughly equivalent distributions, though the distribution of minor pairs with low separations is slightly higher than the major pairs. Thus, secondary halo of minor pairs tend to live slightly closer to their primaries than the  major secondaries.

\todo{quick final conclusions on separations}

\kc{here maybe include a table? what are some values?  z=0,1,2,3,4 and pair frac, sep, vel. ?}

%% separation plots
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{separation_1000.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The redshift evolution of the dwarf pairs closely resembles a power law distribution across the whole redshift range from $z=0-4$.
  At $z=4$, the typical separation between major (minor) dwarf pairs is $42(38)\,\kpc$, and peaks at $z=0$ with a median separation of $128(109)\,\kpc$.
  % Massive Pairs
  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is $81(71)\,\kpc$, to $z=1$, where median separations are $171(124)\,\kpc$. The median separation rises more steeply from z=1 to z=0, peaking around $z=\sim0$ at $288\,\kpc$ and $205\,\kpc$ for major and minor massive pairs respectively.
  % Difference plots
  (Bottom) The median subtracted separation difference between major and minor pairs, and 1-99\% shaded region.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. 
    }
  \label{fig:sep}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{separation_distribution_1000.png}
  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines. 
  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively). However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
    }
  \label{fig:sep-dist}
\end{figure*}

\subsubsection{Relative Velocities}
%% text on velocity vs. redshift plot
We also consider the snapshot-by-snapshot instantaneous relative velocity between each primary and secondary.
We find that the median relative velocity of all pairs (dwarf and massive, major and minor) decreases with decreasing redshift, reaching a minimum at $z=0$ as seen in Fig.~\ref{fig:vel}. 
Though the velocity scales are different, the bulk behavior of dwarf pairs and massive pairs is identical. 
\linebreak
The median velocity of a major dwarf pair decreases approximately linearly from $130$ at $z=4$ to $70\,\kms$ at $z=0$. Likewise, the median velocity for major massive pairs decreases from $260$ at $z=4$ to $170\,\kms$ at $z=0$, albeit less smoothly. 
Fig.~\ref{fig:vel} also includes a panel showing the subtracted median difference at each snapshot of the minor pair from the major pair. Since minor pairs typically have slightly higher velocities than their major pair counterparts, this difference is usually $<\sim0$. The offsets between the relative velocities of dwarf major and minor pairs is between $0-5\,\kms$, and between $0-25\,\kms$ for massive major and minor pairs.

%% text on velocity distribution plot
\kc{left off here\~}
Fig.~\ref{fig:vel-dist}

%% velocity plots 
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{velocity_1000.png}
  \caption{
    (Top) Median relative velocity (in \kms) between the primary and secondary halos of: dwarf pairs (left, green), and massive pairs (right, pink) as a function of redshift. 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
    The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs.
    As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases as well for both dwarf and massive pairs.
    % brief describe
    The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair). 
    % Difference plot
    (Bottom) The median subtracted relative velocity difference between major and minor pairs, and 1-99\% shaded region.
    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\,\kms$ faster than major pairs.
    }
  \label{fig:vel}
\end{figure*}
